Mechanisation of Session-based Lambda Calculus Type Systems

### 2014-11-28 proposal/proposal.tex
Added cofinite quantification changes to Wadler's presentation.

For handling binder freshness, I chose to adopt the cofinite quantification
approach described by~\cite{Aydemir:2008:EFM}~\cite{Aydemir:2008:EFM}, which
excludes a finite set of variables from being considered as the binder. In
contrast, the traditional ``exists-fresh'' approach, where the binder is only
required to be fresh within the abstraction's body, does not produce strong
enough induction principles in some cases. This change will necessitate
changes to the typing rules of GV and CP. Consider for instance the Connect
rule in GV~\cite{Wadler:2014} (Connect) and its corresponding cofinite
quantification version (ConnectCO):

... connect with rule here ... ... connect rule using cofinite quantification

The conclusion binds a variable in Connect but a type in ConnectCO. Thus, in
the premise for ConnectCO one can choose a suitably fresh $x$. The same change is made to the rules for CP so that, for example, output which allocates a fresh variable $y$ no longer names $y$ in the conclusion:

... output in CP ... ... version used here with cofinite quantification ...

Since the name $y$ is assumed to be fresh in the original presentation these
changes do not alter the typing of processes nor the semantics of the
translation from GV to CP. An equivalence between ``exists-fresh'' and
cofinite quantification definitions of the simply-typed $\lambda$ calculus is
given by \citeauthor{Aydemir:2008:EFM}~\cite{Aydemir:2008:EFM}. In general, I
do not aim to formally prove adequacy of the mechanisation.

>>>>

For handling binder freshness, I chose to adopt the cofinite quantification
approach described by~\cite{Aydemir:2008:EFM}~\cite{Aydemir:2008:EFM}, which
excludes a finite set of variables from being considered as the binder. In
contrast, the traditional ``exists-fresh'' approach, where the binder is only
required to be fresh within the abstraction's body, does not produce strong
enough induction principles in some cases. This change will necessitate
changes to the typing rules of GV and CP. Consider for instance the Connect
rule in GV~\cite{Wadler:2014} (C) and its corresponding cofinite
quantification version (CCO):
\input{with-connect-rule}

The conclusion binds a variable in (C) but a type in (CCO). Thus, in the
premise for (CCO) one can choose a suitably fresh $x$ in each premise. Note
that, $L$ can be chosen such that $\Psi \cup \Phi \cup \fv(M) \cup \fv(N)
\subseteq L$, where $\fv(M)$ are the set of free variables in term $M$, and
$x$ can be the same in both premises. Similar changes are made to the rules
for CP so that, for example, output which allocates a fresh variable $y$ no
longer names $y$ in the conclusion: \input{cp-output}

Since the name $y$ is assumed to be fresh in the original presentation these
changes do not alter the typing of processes nor the semantics of the
translation from GV to CP. An equivalence between ``exists-fresh'' and
cofinite quantification definitions of the simply-typed $\lambda$-calculus is
given by \citeauthor{Aydemir:2008:EFM}~\cite{Aydemir:2008:EFM}. In general, I
do not aim to formally prove adequacy of the mechanisation.
